# (PART) Setup {-}

# Setup

## R
Download and install the [latest version of R](https://cran.r-project.org/).

When migrating to a new version of R, this line might help updating packages. 

```{r, eval = FALSE}
update.packages(checkBuilt = TRUE, ask = FALSE)
```


## RStudio

There are a couple of useful settings to change in RStudio. 


* Tools / Global Options / Workspace: Restore .Rdata at startup = OFF
* Tools / Global Options / Workspace: Save workspace to .Rdate on exit = Never


See [Efficient R / Rstudio options](https://csgillespie.github.io/efficientR/set-up.html#rstudio-options) for more information. 

https://csgillespie.github.io/efficientR/set-up.html#rstudio-options


## System dependencies
Windows users: install [RTools](https://cran.r-project.org/bin/windows/Rtools/). 

Mac users: install [Xcode](https://developer.apple.com/xcode/resources/) and [homebrew](https://brew.sh/).

### Spatial packages
To use spatial packages (eg.: `sf`), we need to install some system dependencies. The `sf` [README](https://github.com/r-spatial/sf#installing) has great instructions. Make sure to install these dependencies before trying to install spatial packages.



### R Markdown {#rmd-setup}

Install packages...

```{r, eval = FALSE}
install.packages(c('rmarkdown', 'bookdown', 'knitr'))
```


and use [`tinytex`](https://yihui.org/tinytex/) to get an easy to install and use TeX setup on your computer. 


```{r, eval = FALSE}
install.packages('tinytex')
tinytex::install_tinytex()
```

After installing `tinytex`, make sure to restart RStudio. 


## Git {#git-setup}
Quick setup instructions here, but see the chapter on [Git](#git) for more details. 

### Install git

Check out the great instructions in  [Happy Git With R](https://happygitwithr.com/install-git.html). Be sure to check if `git` is installed first! 

### GitLab

The lab uses primarily [GitLab](https://gitlab.com) for private and group projects and [GitHub](https://github.com) for mirroring published projects or packages. 

1. [Make an account](https://gitlab.com/users/sign_in) on GitLab.com and message me!
1. Setup global git user name and email. See [here](https://happygitwithr.com/hello-git.html). 
1. Setup a local folder on your computer to store all of your git repositories. I use a folder called 'Local-git' under Documents (`/home/alecr/Documents/Local-git`). 

You can alternatively clone your repositories to different places on your hard drive, but I find it more straightforward to keep everything together.

### Git clients

You may opt to use a git client to work with git on a regular basis. Again, see a great discussion in the Happy Git With R book [here](https://happygitwithr.com/git-client.html). We've tried using cross platform clients in the past to make it easy for folks to help each other. These days, it's [GitAhead](https://gitahead.github.io/gitahead.com/). 


