# (PART) Setup {.unnumbered}

# Setup

## R

Download and install the [latest version of
R](https://cran.r-project.org/).

<!-- When migrating to a new version of R, this line might help updating packages.  -->

<!-- update.packages(checkBuilt = TRUE, ask = FALSE) -->

## RStudio

Download and install the [latest version of
RStudio](https://www.rstudio.com/products/rstudio/download/#download).

There are a couple of useful settings to change in RStudio.

-   Tools / Global Options / Workspace: Restore .Rdata at startup = OFF
-   Tools / Global Options / Workspace: Save workspace to .Rdate on exit
    = Never

See [Efficient R / Rstudio
options](https://csgillespie.github.io/efficientR/set-up.html#rstudio-options)
for more information.

## System dependencies

Windows users: install
[RTools](https://cran.r-project.org/bin/windows/Rtools/).

Mac users: install [Xcode](https://developer.apple.com/xcode/resources/)
and [homebrew](https://brew.sh/).

### Spatial packages

To use spatial packages (eg.: `sf`), we need to install some system
dependencies. The `sf`
[README](https://github.com/r-spatial/sf#installing) has great
instructions. Make sure to install these dependencies before trying to
install spatial packages.

You may also find it easier to install using the R-universe version of
packages, for example:

```{r, eval = FALSE}
# Enable this universe
options(repos = c(
  	rspatial = 'https://r-spatial.r-universe.dev',
    r_spatial = 'https://rspatial.r-universe.dev',
    CRAN = 'https://cloud.r-project.org'))

# Install sf and terra packages
install.packages(c('sf', 'terra'))
```

## Literate programming

### Quarto

A new literate programming tool from RStudio has been released for
generating documents, websites, books, etc.

See the [Get Started](https://quarto.org/docs/get-started/) page for
installation instructions.

After installing, check out the [Hello, Quarto
tutorial](https://quarto.org/docs/get-started/hello/rstudio.html).

### R Markdown {#rmd-setup}

Install packages

```{r, eval = FALSE}
install.packages(c('rmarkdown', 'bookdown', 'knitr'))
```

and [`tinytex`](https://yihui.org/tinytex/) helps us get TeX easily
installed on your computer.

```{r, eval = FALSE}
install.packages('tinytex')
tinytex::install_tinytex()
```

After installing `tinytex`, make sure to restart RStudio.

## Git {#git-setup}

Quick setup instructions here, but see the chapter on [Git](#git) for
more details.

### Install git

Check out the great instructions in [Happy Git With
R](https://happygitwithr.com/install-git.html). Be sure to check if
`git` is installed first!

### Hosting services

Historically, the lab primarily uses [GitLab](https://gitlab.com) for
private and group projects and [GitHub](https://github.com) for
mirroring published projects or packages. This was largely dictated by
GitHub's lack of free, private repositories, and GitLab's great
continuous integration tools. Nowadays, the line is less clear - GitHub
offers free private repositories and GitHub Actions. GitHub is more
commonly used, especially in R package development. Take your pick or
use both!

1.  Make an account on
    [GitHub](https://github.com/signup?user_email=&source=form-home-signup)
    or [GitLab](https://gitlab.com/users/sign_in) (or both), and message
    Alec your usernames.
2.  Setup global git user name and email. See
    [here](https://happygitwithr.com/hello-git.html).
3.  Setup a local folder on your computer to store all of your git
    repositories. I use a folder called 'Local-git' under Documents
    (`/home/alecr/Documents/Local-git`).

You can alternatively clone your repositories to different places on
your hard drive, but I find it more straightforward to keep everything
together.

### Git clients

You may opt to use a git client to work with git on a regular basis.
Again, see a great discussion in the Happy Git With R book
[here](https://happygitwithr.com/git-client.html). We've tried using
cross platform clients in the past to make it easy for folks to help
each other. These days a solid recommendation is [GitHub
Desktop](https://desktop.github.com).
