# (PART) Setup {-}

# Setup

## R
Download and install the [latest version of R](https://cran.r-project.org/).

When migrating to a new version of R, this line might help updating packages. 

```{r, eval = FALSE}
update.packages(checkBuilt = TRUE, ask = FALSE)
```


## RStudio


https://csgillespie.github.io/efficientR/set-up.html#rstudio-options


## System dependencies

### Spatial


### R Markdown {#rmd-setup}

Use [`tinytex`](https://yihui.org/tinytex/)


```{r, eval = FALSE}
install.packages('tinytex')
tinytex::install_tinytex()
```


# Git {#git-setup}
Quick setup instructions here, but see the chapter on [Git](Git) for more details. 

## Install git

Check out the great instructions in  [Happy Git With R](https://happygitwithr.com/install-git.html). Be sure to check if `git` is installed first! 

## GitLab

The lab uses primarily [GitLab](https://gitlab.com) for private and group projects and [GitHub](https://github.com) for mirroring published projects or packages. 

1. [Make an account](https://gitlab.com/users/sign_in) on GitLab.com and message me!
1. *Optional:* Setup a local folder on your computer to store all of your git repositories. I use a folder called 'Local-git' under Documents (`/home/alecr/Documents/Local-git`)
1. Setup global git user name and email. See [here](https://happygitwithr.com/hello-git.html). 

## Git clients

You may opt to use a git client to work with git on a regular basis. Again, see a great discussion in the Happy Git With R book [here](https://happygitwithr.com/git-client.html). We've tried using cross platform clients in the past to make it easy for folks to help each other. These days, it's [GitAhead](https://gitahead.github.io/gitahead.com/). 


