# (PART) Data visualization {-}

# ggplot2

```{r, include = FALSE}
library(ggplot2)
data(diamonds)
```

## Facets by chunks of data

Facet wrap using automatically binned values:

"What is going on?!?"

```{r}
ggplot(diamonds, aes(depth, price)) + 
  geom_point()
```

"What if I look at four separate chunks of the data, with approximately the same number of points"

```{r}
ggplot(diamonds, aes(depth, price)) + 
  geom_point() + 
  facet_wrap(~ cut_number(carat, 4))
```

"What if I look at four separate chunks of the data, with the equal ranges in each group?"

```{r}
ggplot(diamonds, aes(depth, price)) + 
  geom_point() + 
  facet_wrap(~ cut_interval(carat, 4))
```

"What if I look at four separate chunks of the data, with a specific width of values in each group?"
```{r}
ggplot(diamonds, aes(depth, price)) + 
  geom_point() + 
  facet_wrap(~ cut_width(carat, 0.5))
```


## Combining plots

the one and only: [`patchwork`](https://patchwork.data-imaginist.com/)

## Slides {#gg-slides}
Workshop: Introduction to ggplot2

Date: November 2 2017

[Slides](https://slides.robitalec.ca/intro-ggplot.html) and  [Resources](https://gitlab.com/robit.a/workshops/-/archive/master/workshops-master.zip?path=intro-ggplot)

```{r, echo = FALSE}
knitr::include_url('https://slides.robitalec.ca/intro-ggplot.html')
```


# Spatial Plotting



# Cool Packages {#viz-cool}

https://ropensci.org/packages/

under vis
