# (PART) Writing {-} 

# Writing

## Writing group
**TODO: (Eric)**


# R Markdown

## Basic markdown

Wrap a word with single asterisks for *italics* and double asterisks for **bold**.

```
Wrap a word with single asterisks for *italics* and double asterisks for **bold**.
```


Surround inline code chunks with single `backticks` or full code blocks with triple backticks:

```r
yum <- is.delicious('gorgonzola')
yum
[1] TRUE
```

Tables can be made with a [markdown table generator](http://www.tablesgenerator.com/markdown_tables#) (or by hand...), or with functions, for example: `knitr::kable`.

```{r, echo = FALSE}
library(data.table)
DT <- data.table(randu)
DT <- DT[1:5]
```

```{r, echo = TRUE, eval = FALSE}
knitr::kable(DT)
```

```{r, echo = FALSE, eval = TRUE}
knitr::kable(DT)
```


**TODO: images**

## Setup

Install packages

```{r, eval = FALSE}
install.packages(c('rmarkdown', 'bookdown', 'knitr')
```

and use [`tinytex`](https://yihui.org/tinytex/)


```{r, eval = FALSE}
install.packages('tinytex')
tinytex::install_tinytex()
```


## YAML


### Rendering multiple output formats

To render multiple output formats from the same R Markdown document, use this example. We remap the knit button / shortcut to rendering all the output formats specified. 

[Example Rmd/render-multiple-formats.Rmd](example-rmd/render-multiple-formats.Rmd)

```yaml
---
title: render-multiple-formats
author: Alec L. Robitaille
output:
   github_document: default
   pdf_document: 
     toc: true
   html_document: default
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
---
```

## BibTeX

### Setting italics in references

Setting italics in your `.bibtex` references is as simple as wrapping the words in `\emph{}`. For example:

```latex
\emph{Escherichia coli}
```

## Presentations With `xaringan`

Yihui Xie made a great package for generating HTML presentations in R Markdown: [`xaringan`](https://bookdown.org/yihui/rmarkdown/xaringan.html). 

All of Alec's slides use this package, see [Slides](Slides). 


### Incremental ggplot slides
An example for building your ggplots incrementally using this example `xaringan` document. 

<script src='https://gitlab.com/snippets/1954903.js'></script>


## Slides {#rmd-slides}
Workshop: Basic R Markdown 

Date: October 21 2019

[Slides](https://slides.robitalec.ca/basic-rmd.html) and [Resources](https://gitlab.com/robit.a/workshops/-/archive/master/workshops-master.zip?path=basic-rmd)

```{r, echo = FALSE}
knitr::include_url('https://slides.robitalec.ca/basic-rmd.html')
```
