# (PART) Writing {-} 

# Writing


# R Markdown

## Basic Markdown

# Markdown syntax

Wrap a word with single asterisks for *italics* and double asterisks for **bold**.

```
Wrap a word with single asterisks for *italics* and double asterisks for **bold**.
```


## Code
Surround inline code chunks with single `backticks` or full code blocks with triple backticks:

```r
yum <- is.delicious('gorgonzola')
yum
[1] TRUE
```

## Tables
Tables can be made with a [markdown table generator](http://www.tablesgenerator.com/markdown_tables#) (or by hand...) or with functions, for example: `knitr::kable`.

```{r, echo = FALSE}
library(data.table)
DT <- data.table(randu)
DT <- DT[1:5]
```

```{r, echo = TRUE, eval = FALSE}
knitr::kable(DT)
```

```{r, echo = FALSE, eval = TRUE}
knitr::kable(DT)
```


## Setup

Install packages

```{r, eval = FALSE}
install.packages(c('rmarkdown', 'bookdown', 'knitr')
```

and use [`tinytex`](https://yihui.org/tinytex/)


```{r, eval = FALSE}
install.packages('tinytex')
tinytex::install_tinytex()
```



## Slides
Workshop: Basic R Markdown 

Date: October 21 2019

[Slides](https://slides.robitalec.ca/basic-rmd.html) and [Resources](https://slides.robitalec.ca/basic-rmd/basic-rmd.zip)

```{r, echo = FALSE}
knitr::include_url('https://slides.robitalec.ca/basic-rmd.html')
```
