# (PART) Writing {-} 

# Writing

## Writing group
**TODO: (Eric)**


# R Markdown

## Basic markdown

Wrap a word with single asterisks for *italics* and double asterisks for **bold**.

```
Wrap a word with single asterisks for *italics* and double asterisks for **bold**.
```


Surround inline code chunks with single `` `backticks` `` or full code blocks with triple backticks:

````
```
yum <- is.delicious('gorgonzola')
yum
[1] TRUE
```
````

Tables can be made with a [markdown table generator](http://www.tablesgenerator.com/markdown_tables#) (or by hand), or with functions, for example: `knitr::kable`.


```{r, echo = TRUE, eval = FALSE}
knitr::kable(diamonds)
```

```{r, echo = FALSE, eval = TRUE}
library(data.table)
library(ggplot2)
data(diamonds)
setDT(diamonds)
knitr::kable(diamonds[1:5])
```



**TODO: images**

## Setup

See [Setup/R Markdown](#rmd-setup).

## YAML
**TODO: link basic YAML Rmd**
**TODO: add classic error not working because tabs instead of spaces**

### Rendering multiple output formats {#rmd-multiple-output}

To render multiple output formats from the same R Markdown document, use this example. We remap the knit button / shortcut to rendering all the output formats specified. 


<script src='https://gitlab.com/snippets/1976028.js'></script>

## BibTeX

### Setting italics in references

Setting italics in your `.bibtex` references is as simple as wrapping the words in `\emph{}`. For example:

```latex
\emph{Escherichia coli}
```

## Reflow lines
If this is a manuscript, and you are noticing everything is on a few really long lines, simply reflow using the shortcut (CTRL+SHIFT+/) or remember to hit enter at the end of a line. 

**TODO: example image of this** 


## Presentations With `xaringan`

Yihui Xie made a great package for generating HTML presentations in R Markdown: [`xaringan`](https://bookdown.org/yihui/rmarkdown/xaringan.html). 

All of Alec's slides use this package, see [Slides](#slides). 


### Incremental ggplot slides
An example for building your ggplots incrementally using this example `xaringan` document. 


<script src='https://gitlab.com/snippets/1954903.js'></script>


## Slides {#rmd-slides}
Workshop: Basic R Markdown 

Date: October 21 2019

[Slides](https://slides.robitalec.ca/basic-rmd.html) and [Resources](https://gitlab.com/robit.a/workshops/-/archive/master/workshops-master.zip?path=basic-rmd)

```{r, echo = FALSE}
knitr::include_url('https://slides.robitalec.ca/basic-rmd.html')
```
