# (PART) Writing {.unnumbered}

# Writing

## Writing group

<!-- **TODO: (Eric)** -->

![](https://img.shields.io/badge/-WIP-yellow.svg)

# R Markdown

Quarto (see below) has been developed to provide some advantages over R
Markdown by including lots of developments and extensions to R Markdown
immediately available in Quarto. See more about the differences
[here](https://quarto.org/docs/faq/rmarkdown.html#quarto-sounds-similar-to-r-markdown.-what-is-the-difference-and-why-create-a-new-project).

## Setup

See [Setup/R Markdown](#rmd-setup).

## Slides {#slides}

October 21 2019 - Basic R Markdown

[Slides](https://slides.robitalec.ca/basic-rmd.html)

[Resources](https://gitlab.com/robitalec/workshops/-/archive/master/workshops-master.zip?path=basic-rmd)

```{r, echo = FALSE}
knitr::include_url('https://slides.robitalec.ca/basic-rmd.html')
```

## Basic markdown

Wrap a word with single asterisks for *italics* and double asterisks for
**bold**.

```         
Wrap a word with single asterisks for *italics* and double asterisks for **bold**.
```

Surround inline code chunks with single `` `backticks` `` or full code
blocks with triple backticks:

````         
```
yum <- is.delicious('gorgonzola')
yum
[1] TRUE
```
````

Tables can be made with a [markdown table
generator](http://www.tablesgenerator.com/markdown_tables#) (or by
hand), or with functions, for example: `knitr::kable`.

```{r, echo = TRUE, eval = FALSE}
knitr::kable(diamonds)
```

```{r, echo = FALSE, eval = TRUE}
library(data.table)
library(ggplot2)
data(diamonds)
setDT(diamonds)
knitr::kable(diamonds[1:5])
```

<!-- **TODO: images** -->

## YAML

![](https://img.shields.io/badge/-WIP-yellow.svg)

<!-- **TODO: link basic YAML Rmd** -->

<!-- **TODO: add classic error not working because tabs instead of spaces** -->

### Rendering multiple output formats {#rmd-multiple-output}

To render multiple output formats from the same R Markdown document, use
this example. We remap the knit button / shortcut to rendering all the
output formats specified.

```{=html}
<script src='https://gitlab.com/snippets/1976028.js'></script>
```

## BibTeX

### Setting italics in references

Setting italics in your `.bibtex` references is as simple as wrapping
the words in `\emph{}`. For example:

``` latex
\emph{Escherichia coli}
```

## Tables

![](https://img.shields.io/badge/-WIP-yellow.svg)

Lots of options are available for generating markdown tables from R
objects, or text.

Manually/copy-paste

-   [Tables Generator](https://www.tablesgenerator.com/markdown_tables)

R packages

-   `knitr::kable`
-   [`pander`](http://rapporter.github.io/pander/)
-   [`gt`](https://gt.rstudio.com/)
-   [`flextable`](https://ardata-fr.github.io/flextable-book/)
-   [`xtable`](https://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf)

Note: differences between these packages are mainly in syntax but more
importantly also in the possible output formats. Some only work with
HTML output, some only PDF, etc.

## Reflow lines

If this is a manuscript, and you are noticing (especially in Git)
everything is on a few really long lines, simply reflow using the
shortcut (CTRL+SHIFT+/) or remember to hit enter at the end of a line.

<!-- **TODO: example image of this**  -->

## Presentations with `xaringan`

Yihui Xie made a great package for generating HTML presentations in R
Markdown:
[`xaringan`](https://bookdown.org/yihui/rmarkdown/xaringan.html).

All of Alec's slides use this package, see [Slides](#slides).

### Incremental ggplot slides

An example for building your ggplots incrementally using this example
`xaringan` document.

```{=html}
<script src='https://gitlab.com/snippets/1954903.js'></script>
```

<!-- ## Manuscript notes -->

<!-- use PDF for supplements, latex changes for fig caps -->

<!-- flextable for office tables -->

# Quarto

![](https://img.shields.io/badge/-WIP-yellow.svg)

# Reference management tools

## Zotero

![](https://img.shields.io/badge/-WIP-yellow.svg)

<!-- **TODO: zotero/mendeley** -->
