# (PART) Etc {.unnumbered}

# Slides

## An Introduction to Remote Sensing with Earth Engine

Date: December 10 2020

Alec L. Robitaille and Isabella C. Richmond

[Resources](https://github.com/robitalec/workshops/tree/master/ee),
[Slides](https://slides.robitalec.ca/ee.html)

```{r, echo = FALSE}
knitr::include_url('https://slides.robitalec.ca/ee.html')
```

## Some Reproducibility

Date: August 4 2020

Alec L. Robitaille

[Resources](https://github.com/robitalec/workshops/tree/master/some-reproducibility),
[Binder](https://mybinder.org/v2/gl/robit.a%2Fsome-reproducibility-example/master?urlpath=rstudio)

## Git and Projects

Date: February 6 2020

Alec L. Robitaille

[Slides](https://slides.robitalec.ca/git-and-projects.html) and
[Resources](https://gitlab.com/robitalec/workshops/-/archive/master/workshops-master.zip?path=git-and-projects)

```{r, echo = FALSE}
knitr::include_url('https://slides.robitalec.ca/git-and-projects.html')
```

## Basic R Markdown

Date: October 21 2019

Alec L. Robitaille

[Slides](https://slides.robitalec.ca/basic-rmd.html) and
[Resources](https://gitlab.com/robitalec/workshops/-/archive/master/workshops-master.zip?path=basic-rmd)

```{r, echo = FALSE}
knitr::include_url('https://slides.robitalec.ca/basic-rmd.html')
```

## Developing R Packages

Date: October 25 2018

Alec L. Robitaille

[Slides](https://slides.robitalec.ca/r-packages.html) and
[Resources](https://gitlab.com/robitalec/workshops/-/archive/master/workshops-master.zip?path=r-packages)

```{r, echo = FALSE}
knitr::include_url('https://slides.robitalec.ca/r-packages.html')
```

## Functions in R

Date: October 25 2018

Alec L. Robitaille

[Slides](https://slides.robitalec.ca/functions-in-r.html) and
[Resources](https://gitlab.com/robitalec/workshops/-/archive/master/workshops-master.zip?path=functions-in-r)

```{r, echo = FALSE}
knitr::include_url('https://slides.robitalec.ca/functions-in-r.html')
```

## Introduction to data.table

Date: November 16 2017

Alec L. Robitaille

[Slides](https://slides.robitalec.ca/intro-data-table.html) and
[Resources](https://gitlab.com/robitalec/workshops/-/archive/master/workshops-master.zip?path=intro-data-table)

```{r, echo = FALSE}
knitr::include_url('https://slides.robitalec.ca/intro-data-table.html')
```

## Introduction to ggplot2

Date: November 2 2017

Alec L. Robitaille

[Slides](https://slides.robitalec.ca/intro-ggplot.html) and
[Resources](https://gitlab.com/robitalec/workshops/-/archive/master/workshops-master.zip?path=intro-ggplot)

```{r, echo = FALSE}
knitr::include_url('https://slides.robitalec.ca/intro-ggplot.html')
```
